|

### 2023-11-15 manuscript/manuscript_1.0.Rmd
submitted version 1.0

   \large \textbf{Title:} The role of learning in the evolution of status signalling: a modeling approach
subtitle: |
  \normalsize \textbf{Abbreviated title:} Learning and evolution in status signalling
author: 

@@

@@

keywords: My keywords

@@

editor_options:
  markdown:
    wrap: 80
---

@@

@@

# Top panels -  A the sender code and  B learning for the receiver code
# load(here("manuscript","manuscript_1.0_cache","latex","modelStruc_6905f4797a1faa21041511a8dcdf1eb9.RData"))
library(dplyr)
honestBig<-readPNG(here("Images/cart_honestBig.png"))
honestSmall<-readPNG(here("Images/cart_honestSmall.png"))
dishonest<-readPNG(here("Images/cart_dishonest.png"))
par(plt=posPlot(numplotx = 2,idplotx = 1,numploty = 1,idploty = 1,upboundx = 91,
                lowboundy = 18),
    las=1,mfrow=c(2,1),mgp=c(2,0.7,0))
  rangPars<-data.frame(honest=c(4,2),dishonest=c(0,0))
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangPars,function(x)logist(rangQual,alpha = x[2],beta = x[1]))
 plot(0,0,type="l",xlab="",xlim=c(0,1),
      ylab ="",cex.lab=1,lwd=2,col="grey",cex.axis=1,ylim=c(0,1.1),xaxt="n")
 axis(1)
 text(x = 0.08,y=1.05,"A",cex = 1.5)
 mtext("Quality",1,line = 1.5,cex = 1,las = 0)
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 mtext("Badge size",2,line = 2,cex = 1,las = 0)
 # include bird cartoons
 rasterImage(honestBig,0.75,0.87,0.95,1.07)
 rasterImage(honestSmall,0.05,0.01,0.25,0.21)
 rasterImage(dishonest,0.75,0.5,0.95,0.7)
 rasterImage(dishonest,0.05,0.5,0.25,0.7)
 # legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")

>>>>

   The role of learning in the evolution of status signaling: a modeling approach
# subtitle: |
#   \normalsize \textbf{Abbreviated title:} Learning and evolution in status signalling

@@

    \providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}

@@

keywords: |
  Biological signals, evolutionary branching, agent-based modeling, animal communication, badges of status,
  handicap principle

@@

editor_options:
  markdown:
    wrap: 80

```{=latex}
\keywords{Signals, evolutionary branching, agent-based modeling, animal communication, badges of status, handicap principle}
```

@@

The code necessary to run simulations as well as to produce visualizations can be found 
in: \url{https://doi.org/10.5281/zenodo.8359809}

@@

# Top panels -  A the sender code and  B learning for the receiver code
# load(here("manuscript","manuscript_1.0_cache","latex","modelStruc_6905f4797a1faa21041511a8dcdf1eb9.RData"))
library(dplyr)
honestBig<-readPNG(here("Images/cart_honestBig.png"))
honestSmall<-readPNG(here("Images/cart_honestSmall.png"))
dishonest<-readPNG(here("Images/cart_dishonest.png"))
par(plt=posPlot(numplotx = 2,idplotx = 1,numploty = 1,idploty = 1,upboundx = 91,
                lowboundy = 18),
    las=1,mfrow=c(2,1),mgp=c(2,0.7,0))
  rangPars<-data.frame(honest=c(4,2),dishonest=c(0,0))
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangPars,function(x)logist(rangQual,alpha = x[2],beta = x[1]))
 plot(0,0,type="l",xlab="",xlim=c(0,1),
      ylab ="",cex.lab=1,lwd=2,col="grey",cex.axis=1,ylim=c(0,1.1),xaxt="n")
 axis(1)
 text(x = 0.08,y=1.05,"A",cex = 1.5)
 mtext("Quality",1,line = 1.5,cex = 1,las = 0)
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 mtext("Badge size",2,line = 2,cex = 1,las = 0)
 # include bird cartoons
 rasterImage(honestBig,0.77,0.87,0.95,1.07)
 rasterImage(honestSmall,0.05,0.01,0.22,0.21)
 rasterImage(dishonest,0.77,0.5,0.95,0.7)
 rasterImage(dishonest,0.05,0.5,0.22,0.7)
 # legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")
